Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-02-28 size_differentiated_export.tex
Updates from Overleaf

\subsection{Particle tracking}

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking. In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate, as it reduces the chances of particles being re-entrained into the mixed layer the following winter. We first consider the case of conservatives particles that do not remineralize in order to better identify the effects of ocean dynamics and spectral slope on export.

The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).

%FIG6
\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export}
	\caption{Percentage of particles located below 100 m as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Expected percentages of exported particles based on only gravitational sinking are indicated with dashed lines.}
	\label{fig: particle_export}
\end{figure}

>>>>

\subsection{Gravitational and Advective Sinking of POC}

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking. In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2018}. We first consider the case of conservatives particles that do not remineralize in order to isolate the effects of ocean dynamics on export.

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles, is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\% of total export). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}).

\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
%The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).

%FIG6
\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	\caption{Upward (top) and downward (bottom) fluxes of particles at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are  For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\label{fig: particle_export}
\end{figure}
